\documentclass{article}
\usepackage[left=0.75in, right=0.75in, bottom=0.75in, top=0.75in]{geometry}
\usepackage{tabu}
\pagestyle{empty}
\begin{document}

\noindent\textbf{\large{Silva, Ryan J Capt USAF USAFA HQ USAFA/DFEC}}

\noindent\makebox[\linewidth]{\rule[5mm]{\linewidth}{3.5pt}}

\noindent \begin{tabu} to \textwidth{l X[l]}

    \textbf{From:} & Solti, James P Civ USAF USAFA USAFA/DFER\\ 
    \textbf{Sent:} & Thursday, September 26, 2013 3:34 PM \\
    \textbf{To:} &  Silva, Ryan J Capt USAF USAFA HQ USAFA/DFEC \\
    \textbf{Cc:} & MILLER, ERIN M CTR USAF USAFA DF/DFER; Kraus, Robert J Mil Col USAF USAFA USAFA/DFE \\
    \textbf{Subject:} & FW: GNU General Public License \\
    \textbf{Signed By:} & james.solti.1@us.af.mil \\
\end{tabu}
\hspace{0pt} \\

Capt Silva, \\

The proposed effort seems within bounds, subject to the constraints below.
In addition, please remind cadets of Personally Identifiable Information
(PII) considerations. \\

VR, \\

Dr. S- \\

\noindent Dr. Jim Solti \\
Deputy Director of Research \\
Assistant Professor \\
U.S. Air Force Academy \\
719-333-2853 (office) \\
850-598-0191 (cell) \\


\noindent-----Original Message----- \\

\noindent \begin{tabu} to \textwidth{l X[l]}

    \textbf{From:} & MCLAUTHLIN, SCOTT B GS-13 USAF USAFA USAFA/JA [mailto:scott.mclauthlin@us.af.mil]\\ 
    \textbf{Sent:} & Tuesday, September 10, 2013 7:55 AM \\
    \textbf{To:} & MILLER, ERIN M CTR USAF USAFA DF/DFER; Kraus, Robert J Mil Col USAF USAFA USAFA/DFER \\
    \textbf{Cc:} & Solti, James P Civ USAF USAFA USAFA/DFER; Silva, Ryan J Capt USAF USAFA HQ USAFA/DFEC \\
    \textbf{Subject:} & RE: GNU General Public License \\
\end{tabu}
\hspace{0pt} \\

Erin - I don't see any problems with pressing on as long as this all stays open source.  Also, think the instructions cadets are receiving look good and appropriate. \\

Scott \\

\noindent Scott B. McLauthlin \\
Attorney Advisor \\
USAFA JA \\
8034 Edgerton Drive, Suite 237 \\
USAF Academy CO 80840 \\
DSN 333-9606; Comm (719) 333-9606; Fax 3-3011 \\

\newpage
\noindent-----Original Message----- \\

\noindent \begin{tabu} to \textwidth{l X[l]}

 \textbf{From:} & MILLER, ERIN M CTR USAF USAFA DF/DFER [mailto:erin.miller.ctr@usafa.edu]  \\
 \textbf{Sent:} & Monday, September 09, 2013 1:55 PM \\
 \textbf{To:} & Kraus, Robert J Mil Col USAF USAFA USAFA/DFER; MCLAUTHLIN, SCOTT B GS-13 USAF USAFA USAFA/JA \\
 \textbf{Cc:} & Solti, James P Civ USAF USAFA USAFA/DFER; Silva, Ryan J Capt USAF USAFA HQ USAFA/DFEC \\
 \textbf{Subject:} & FW: GNU General Public License \\
\end{tabu}
\hspace{0pt} \\
Col Kraus, Scott, \\

Please take a look at the below. Please advise whether Capt Silva should press on. Also, any additional instructions to cadets would be helpful. \\

V/r \\

Erin \\

\noindent Erin M. Miller \\
Research Programs Manager \\
DSN: 333-3311 COMM: (719) 333-3311 \\
Office of Research, USAFA/DFER \\
2354 Fairchild Drive, Suite 2H29 \\
USAF Academy, CO 80840 \\
Apogee Engineering in support of USAFA \\
\hspace{0pt} \\
%\newpage
\noindent-----Original Message----- \\

\noindent \begin{tabu} to \textwidth{l X[l]}
 
  \textbf{From:} & Silva, Ryan J Capt USAF USAFA HQ USAFA/DFEC  \\
  \textbf{Sent:} & Monday, September 09, 2013 1:21 PM \\
  \textbf{To:} & MILLER, ERIN M CTR USAF USAFA DF/DFER \\
  \textbf{Subject:} & GNU General Public License \\
\end{tabu}
\hspace{0pt} \\

Erin, \\

Can I lead cadets in contributing to Open Source research that uses Open-Source software? The source code for open source software is freely published and freely distributed under the GNU Public License. \\
 \\
The code repository the cadets would primarily use is physionet. The link to the physionet licensing details is below: \\

http://www.physionet.org/faq.shtml\#license \\

\noindent The FAQ states: "The software is licensed under the 'GNU Public License'". This license agreement can be found at: \\

http://www.gnu.org/licenses/gpl.html \\

\noindent The definition of "Open-Source" can be found here: \\

http://opensource.org/docs/definition.php \\

\newpage
\noindent All software comes with the following header: \\
 \\
\% \\
\%    This program is free software; you can redistribute it and/or modify \\
\%    it under the terms of the GNU General Public License as published by \\
\%    the Free Software Foundation; either version 2 of the License, or \\
\%    (at your option) any later version. \\
\% \\
\%    This program is distributed in the hope that it will be useful, \\
\%    but WITHOUT ANY WARRANTY; without even the implied warranty of \\
\%    MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the \\
\%    GNU General Public License for more details. \\
\% \\
\%    You should have received a copy of the GNU General Public License \\
\%    along with this program; if not, write to the Free Software \\
\%    Foundation, Inc., 59 Temple Place, Suite 330, Boston, MA  02111-1307USA \\
\%  \\

\noindent Cadets will be instructed that UNDER NO CIRCUMSTANCES should proprietary intellectual property be included in Open-Source software. \\
\hspace{0pt} \\
\noindent Do you think this is acceptable? \\

\noindent Thanks so much for the help! \\

\noindent Very Respectfully, \\
Capt Ryan Silva \\
USAFA/DFEC \\
Falcon 50 Race Director \\
333-6973 \\
\end{document}
